Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-24 paper/paper.Rmd
paper tweaks

author-note:
    "Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(ggplot2)
library(BayesFactor)
library(ggrepel)
#devtools::install_github("langcog/langcog")
library(langcog)
library(cowplot)
library(png)
```

@@

With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy. This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments. Nevertheless, there are significant limitations on what can be done in the course of a single term and within the constraints of a course budget. We return in the Discussion to limitations on our approach.

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could easily be reproduced by a motivated student.

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings. A summary of the original findings is given in Table \ref{tab:summary}.

@@

To ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH). In addition to as-needed guidance, each student collected two pilot samples. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being logged by the experiment and that analytic scripts for the confirmatory analyses functioned appropriately. After pilot A was completed, the instructor or a TA reviewed the student's experiment (acting as a participant) and critiqued and reviewed the student's full analytic code and output.

@@

After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change. Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework. In addition, prior to data collection, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).

@@

Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. In one case, the original experiment was  extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In one case, we reduced the number of trials as part of the adaptation to Mechanical Turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).

@@

Students chose findings from a wide variety of domains for replication. One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015]. Details of individual replications are available in SOM.

@@

Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student failed to complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review).

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students were `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rllllllll}
  \hline
\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
  \hline
   &  & No & Yes & Yes & No & No & Some & Yes \\ 
  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
  \hline
  Total & 11 & 6 & 5 & 5 & 6 & 4 & 2 & 5 \\
   \hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.}
\end{table}

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\%
vs. 
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%. 
) and having open materials (
`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. 
`r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

@@

Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways. The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes and allows for a more fine-grained comparison across studies than a binary significance criterion. The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961]. Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016, @wagenmakers2016].  While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).

@@

@@

In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*. We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal. Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing. The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but results were not statistically significant and had both smaller effect size and lower evidential value than the originals.

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants. Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects.

Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate of replication?

Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013,@ioannidis2005]. On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016]. For both reasons of design and scale, our study here cannot disentangle these factors empirically. Nevertheless, the consistent decreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that initial publications tend to over-estimate effects. And although our sample was too small for statistical inference, numerically our results do not support replication fidelity in terms of sample and procedure as a primary driver of success.

@@

Indeed, by the standards of clinical trials research, every single study we replicated in this report would be classified as exploratory research. No protocol was pre-registered, and the pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.  Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications. And in many cases, there are no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf. @bakeman2005]. This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging.

@@

# Supplemental Materials: Project-By-Project Methods Addendum

```{r, fig.height=9, fig.width=6}
  # colors:268bd2 859900 dc322f
library(png)
layout(matrix(1:24,nr=6,byr=T))
project_key_sorted <- c(
  "jsalloum","ehermann","salehi", # rep = 1
  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
  "jreynolds","jmarias","auc" #rep = 0
)
for (key in project_key_sorted) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

@@

For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication.

>>>>

author-note:
    "These authors contributed equally. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(ggplot2)
library(BayesFactor)
library(ggrepel)
#devtools::install_github("langcog/langcog")
library(langcog)
library(cowplot)
library(png)
```

@@

With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy. This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments. Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget. We return in the Discussion to limitations on our approach.

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- at least as far as support for the same theoretical claims -- by a motivated student.

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students. A summary of the original findings is given in Table \ref{tab:summary}.

@@

To ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH). In addition to as-needed guidance, each student collected two pilot samples. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately. After Pilot A was completed, the instructor or a TA reviewed the student's experimental script (acting as a participant) and critiqued and reviewed the student's full analytic code and output.

@@

After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made any requested changes. Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework. In addition, prior to data collection, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).

@@

Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. In one case, the original experiment was  extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In one case, we reduced the number of trials as part of the adaptation to Mechanical Turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).

@@

Students chose findings from a wide variety of domains for replication. One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015]. Details of individual replications are available in SOM.

@@

Of the 15 students in the class, all completed projects (two with extensions, one short and one more significant), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student failed to complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review).

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rl|ccccccc}
  \hline
\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
  \hline
   &  & No & Yes & Yes & No & No & Some & Yes \\ 
  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
  \hline
  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
   \hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.}
\end{table}

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

@@

Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways. The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes and allows for a more fine-grained comparison across studies than a binary significance criterion. The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961]. Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016;@wagenmakers2016].  While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).

@@

This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well. Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g. BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.

@@

In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*. We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal. Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing. The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants. Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.

Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate?

Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013,@ioannidis2005]. On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016]. For both reasons of design and scale, our study here cannot disentangle these factors empirically. Nevertheless, the consistent decreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that initial publications tend to over-estimate effects. However, in addition, although our sample was too small for statistical inference, numerically our results support replication fidelity in terms of sample and procedure as having some effects on success.

@@

Indeed, by the standards of clinical trials research, nearly every study we replicated in this report would be classified as exploratory research. No protocol was pre-registered, and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.  Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications. And in many cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf. @bakeman2005]. This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging.

@@

# Appendix: Project-By-Project Methods Addendum

```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side comparison of plots for each attempted replication. All error bars are standard error of the mean. Original data were estimated from figures when not otherwise available. Replications are sorted and color coded by subjective replication success."}
  # colors:268bd2 859900 dc322f
library(png)
layout(matrix(1:24,nr=6,byr=T))
project_key_sorted <- c(
  "jsalloum","ehermann","salehi", # rep = 1
  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
  "jreynolds","jmarias","auc" #rep = 0
)
for (key in project_key_sorted) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

@@

For each project, we present a summary of the finding, the key statistical test, and the impressionistic outcomes of the replication. Figure 3 shows a side-by-side comparison of the key visualization for each study.
